Stock forecasting methods and their usage

### 2015-06-01 Paper_self.tex
added description of first algorithm

We investigated algorithms that bring good results with time series analysis. The computer programs we implemented were specialized  making a good prediction only looking at one single stock and its trend. These algorithms were tested on real stock data we fetched from the yahoo finance API. 
\\
We used yahoo finance because it gives easy access to numerous stocks and their historical prices. The API yahoo grants is pretty simple. The only thing you have to do to download the data you need is, preparing a link so it fits your needs. For example the link: 
\\
\textit{\url{http://real-chart.finance.yahoo.com/table.csv?s=IBM&a=00&b=2&c=1962&d=04&e=21&f=2015&g=d&ignore=.csv}}
\\
 provides the data in a csv-file. The stock that this link is going to download is IBM (International Business Machines Corporation). It is also possible to adjust the timespan and format of the data. 
This method of getting historical stock market data is pretty easy to implement in various programming languages. It is also possible to download the csv-file to your computer with this link.
\\
After we got the data we needed, we started implementing the algorithms that we thought of. % beschreiben wie der algorithmus von Herr Fischer funktioniert und die 2-3 die wir noch implementiert haben

% needed in second column of first page if using \IEEEpubid
%\IEEEpubidadjcol

@@

\section{Conclusion}
\blindtext

@@

\appendices
\section{Proof of the First Zonklar Equation}
\blindtext

>>>>

We investigated algorithms that bring good results with time series analysis. The computer programs we implemented were specialized  making a good prediction only looking at one single stock and its trend. These algorithms were tested on real stock data we fetched from the yahoo finance API. 
\\
We used yahoo finance because it gives easy access to numerous stocks and their historical prices. The API yahoo grants is pretty simple. The only thing you have to do to download the data you need is, preparing a link so it fits your needs. For example the link: 
\\
\textit{\url{http://real-chart.finance.yahoo.com/table.csv?s=IBM&a=00&b=2&c=1962&d=04&e=21&f=2015&g=d&ignore=.csv}}
\\
 provides the data in a csv-file. The stock that this link is going to download is IBM (International Business Machines Corporation). It is also possible to adjust the timespan and format of the data. 
This method of getting historical stock market data is pretty easy to implement in various programming languages. It is also possible to download the csv-file to your computer with this link.
\\
After we got the data we needed, we started implementing the algorithms that we thought of.

% beschreiben wie der algorithmus von Herr Fischer funktioniert und die 2-3 die wir noch implementiert haben

\section{Algorithms}

We implemented three different algorithms to predict stock prices and maximise the outcome. All three of them only consider one stock at a time. In this section we will describe the algorithms we used

\subsection{Algorithm using the latest trend}

TODO: algorithmus beschreiben mit dem neuesten Trend der beispielweiße die nächsten 5 tage vorraussagen kann.

\subsection{Algorithm using long term moving average}

This algorithm is based on analysing the moving average of a stock. It does not make a prediction about the precise prise of a stock the next day. The only thing it does, is giving an advice when to buy a stock and when to sell it. If you follow the advices of this algorithm, it is possible to have a positive outcome even if the trend of a stock is overall going down.
\\
The first thing we had to do was calculating the moving average of a stock. This can be computed as below-
\\
\\
$ MA_{n} =  \frac{C_{D} + C_{D-1} + ... + C_{D-(n-1)}}{n} $
\\
\\
Where C is the closing price of a stock on a specific day D.

Now we need to calculate MA$ _{50} $\footnote{Moving average of the last 50 days} and MA$ _{200} $\footnote{Moving average of the last 200 days} of a specific stock we want to invest in.
\\
If the condition MA$ _{50} >$  MA$ _{200} $ is fulfilled the algorithms gives the advice to buy the stock on this day. After the stock has been bought, the algorithm checks every day if the requirement is still met. As soon as MA$ _{50} <$  MA$ _{200} $ the algorithm recommends to sell the stock. This algorithm seems to be very simple but it is worth noticing, that the outcome was pretty solid in the test we made. For detailed results, see chapter \ref{results} on page  \pageref{results}.

\subsection{Algorithm using neuronal network}

This algorithm is based on neuronal networks.

TODO: den algorithmus von Herr Fischer beschreiben.

\section{Results}
\label{results}
% needed in second column of first page if using \IEEEpubid
%\IEEEpubidadjcol

@@

\section{Conclusion}

\section{Future Work}

@@

\appendices
\section{Proof of the First Zonklar Equation}
